%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%\documentclass[]{friggeri-cv} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{ly-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\begin{document}
\header{liang}{yu}{Software Engineer} % Your name and current job title/field
%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------
\begin{aside} % In the aside, each new line forces a line break
\section{contact}
22 Orient Street
Malden, MA 02148
United States
~
(617) 901 0618
~
\href{mailto:yuliang.name@gmail.com}{yuliang.name@gmail.com}
\href{http://www.linkedin.com/in/liangyu2012neu}{LinkedIn: Liang Yu}
\section{programming languages}
Java c cpp python
shell c\# \LaTeX
\section{operating system}
Mac OS X Ubuntu iOS
Android Windows
\section{web services}
Javascript 
CSS3 HTML5 ActionScript
Dojo GWT GXT Ajax
REST SOAP Flex
\section{development tools}
Eclipse SublimeText VIM
VisualStudio Fiddler GDB
GIT SVN Windows Azure
Hadoop MapReduce Xen
Jenkins MySQL Firebug
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2010-2012}
{Masters of Science} 
%{Masters {\normalfont of Science}}
{Northeastern Unviersity, Boston, United States}
{Computer Science \hspace{4mm} \footnotesize{GPA 3.54/4.0}}
%{\emph{Computer Science} \\ \footnotesize{GPA 3.5/4.0}}
%------------------------------------------------
\entry
{2005-2009}
{Bachelor of Science}
{Nanchang University, Nanchang, China}
{Information and Computational Science}
%------------------------------------------------
\end{entrylist}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{experience}
\begin{entrylist}
%------------------------------------------------
\entry
{2013-Now}
{Integrated Computer Solutions}
{Bedford, Massachusetts}
{\emph{Mobile Software Developer}\\
Inkarus Game
\begin{itemize}
  \item Modified existed Code to plugin advertisements in the Game by leveraging the Microsfot Advertsing SDK.
  \item used the WinJS library and HTML 5 to added two dialogs to submit results to the Windows Azure serve and retrieve the others' result from the serve.
  \item fixed minor bugs in the legacy codes.
\end{itemize}
Questia
\begin{itemize}
  \item Levaged the Model-View-Viewmodel, Service Locator design pattern in development.
  \item used XAML to build the Project page and C\# to setup data model as the datasource for the page.
  \item used the Fiddler to inspect the data transfer in the network.
\end{itemize}}
%------------------------------------------------
\entry
{2012}
{Acme Packet}
{Bedford, Massachusetts \small{(Eight Months)}}
{\emph{Co-op Enginner Intern}
\begin{itemize}
  \item Helped with ASC automated testing framework by writing twenty pyton tests on SIP protocol.
	\item Identified bugs in four existing web services application, which were written separately in Java, GWT/GXT, JavaScript and Flex
  \item Developed the Call-Transfer web services application with JavaScript and Dojo API.
	\item Implemented performance tests in Python scripts to measure product performance.
  \item Enhanced the quality of an existing iOS mobile application by fixing two bugs and improved its UI and workflow by implementing good interface design principles.
\end{itemize}}
%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{relevant coursework}

\begin{entrylist}
%------------------------------------------------Analyzing Company Stock Prices Via Twitter Posts
\entry
{graduate}
{Big Data, Cloud Computing}
{Northeastern University}
{courses: \emph{Parallel Computing in MapReduce, Introduction to Database}\vspace*{4pt}\\
projects: Analyzing Company Stock Prices Via Twitter Posts
%{\footnotesize{\emph{Parallel Computing in MapReduce, Introduction to Database}} \\
\begin{itemize}
      \item Developed this project in Eclipse and ran it on a ten-node cluster.
      \item Implemented Java codes to map emotional words to numerical scale.
      \item Processed 1.7 billion twitter messages and 50 millions stock records with Hadoop APIs and Pig scripts.
      \item Analyzed the relationship between the content of the tweets for 11 individual comapanies within certain days and thieir stock prices on the following day and renderd the results in graphs by using HTML and CSS.
\end{itemize}}
%------------------------------------------------
\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{Computer System}
{Northeastern University}
{courses: \emph{Computer System, High Performance Computing}\vspace*{4pt}\\
projects: XXXXXX
\begin{itemize}
       \item Implemented POSIX thread libraries to solve the Ferry-Traveler Problem and used mutex to deal with synchronized issues between different threads.
       \item Wrote c codes to mimic device-related operations the mirroring, striping, RAID4 and RAID5 operations.
       \item Implemented a file system with basic methods(mkdir, rm, read, write and ls).
\end{itemize}}
%------------------------------------------------
\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{Software Design}
{Northeastern University}
{courses: \emph{Program Design Paradigms, Managing Software Development}\vspace*{4pt}\\ 
projects: XXXXXXXX
\begin{itemize}
	\item Wrote an avatar that can solve a scientific problem and propose the result to the Server and implemented JUnit test on the major functions.
	\item Used Jenkins continuous integration system to ensure the independence of builds and test cases and measure test coverage in the SCG project.
	\item Followed software development cycle principle in development and used singleton, Factory and MVC design pattern in development.
\end{itemize}}
%------------------------------------------------
\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{Algorithms}
{Northeastern University}
{\emph{Algorithms, Advanced Algorithms}}\\
%------------------------------------------------
\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{\small{undergraudate}}
{}
{Nanchang University}
{courses: \\ \emph{C Programming Language, Data Structures,\\Assemble Language(IBM), Introduction to Linux}}
%------------------------------------------------
\end{entrylist}
\end{document}