\documentclass[margin,line]{res}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0.05in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\pagestyle{empty}
\begin{document}
\vspace{-2cm}
\name{Liang Yu \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
Woburn & {\it E-mail:}  yuliang.name@gmail.com \\
Masschusetts  & {\it website:} www.yuliang.xyz \\     
\end{tabular}

\section{\sc Computer\\Skills}
\begin{list2}
\item {\bf Programming Languages:} C, C++, Java, Python, Linux Shell, tcl, \LaTeX
\item {\bf Development Tools:} Vim, Sublime Text, Eclipse, GDB, Valgrind
\item {\bf Operating Systems:}  Unix/Linux, Mac OSX, iOS, Android, Windows
\item {\bf Networking:} Wireshark, Fiddler, SIP, TCP/IP, TLS/DTLS,
                  SSL, RTP, DNS, VLAN, Sipp
\item {\bf Web Development:} Javascripts, CSS3, HTML5, Bootstrap, Tomcat,
                       REST, Flex, Dojo, Ajax, GWT
\item {\bf Version Control:} GIT, SVN, Jenkins, Jira, ClearCase
\item {\bf Cloud Computing:} MySQL, Hadoop, MapReduce, Windows Azure\\
\end{list2}

\section{\sc Work\\Experience}
{\bf Oracle America Inc.}, Bedford, Massachusetts USA

\vspace{-.3cm}
{\em SQA Analyst} \hfill {Since 2014.2}\\
\begin{itemize}
\item Desgined functional, integratoin and regression test plans for various features
of Session Border Controller Products.
\item Wrote tcl scripts to run the unit tests.
\item Wrote performance test plans and set up devices for performance tests.
\item Analyzed the results of performance tests to identify scale, performance and
stabilty aspects before codes were released.
\end{itemize}

% ICS
{Integrated Computer Solutions}, Bedford, Massachusetts USA

\vspace{-.3cm}
{\em {\bf Software Developer}} \hfill {2013.4 - 2014.2}\\
Topics (Android App)
\begin{itemize}
\item Wrote a NetworkManager Class to provide clear and convenient access to the Topic server.
\item Implemented fourteen AsyncTask subclassed to call the REST API and parse the response
in JSON format.
\item Bridged the UI Components and the datasources by extending Android BaseAdapter class
\item Built the UI with fragments and navigation drawer.
\item Implemented unit tests for APIs with pytest in Ubuntu environment.
\end{itemize}

Inkarus Game (HTML5 and Javascript Game)
\begin{itemize}
\item Added three advertisement banners in the GameOver page by leveraging
the Microsoft Advertising SDK.
\item Submitted the score and screenshot of the solution to Windows Azure cloud
and rendered data from cloud to users by using WinJS library and HTML5.
\item Fixed animation bugs in the legacy codes.
\end{itemize}

% Acme Packet
{\bf Acme Packet}, Bedford, Massachusetts USA

\vspace{-.3cm}
{\em \bf {Software Developer Intern}} \hfill {2012.1 - 2012.8}\\
\begin{itemize}
\item Helped with ASC automated testing framework by wrting twenty Python unit tests on SIP protocol
\item Identified and fixed bugs in four existing web services applications.
\item Developed the Call-Transfer web services application with JavaScript and Dojo API.
\item Enhanced the quality of an existing iOS mobile application by fixing two bugs and improved its UI and workflow by implementing good interface design principles.
\end{itemize}

\section{\sc Education}
{\bf Northeastern University}, Boston, Massachusetts USA

\vspace{-.3cm}
{\em Master of Science, Major in {\bf Computer Science}} \hfill {2010.9 - 2012.12}\\

{\bf Nanchang University}, Nanchang, Jiangxi China

\vspace{-.3cm}
{\em Bachelor of Science, Major in {\bf Mathematics}} \hfill {2005.9 - 2009.6}\\

%\vspace*{-.25in}
%\begin{verbatim}http://www.nist.gov/speech/publications/tw00/html/abstract.htm#cp1-50\end{verbatim}

\end{resume}
\end{document}
