\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\textheight=11in
\pagestyle{empty}
%\raggedbottom
\raggedright

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt}  \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \large{ \textbf{#1}\hfill #2\\ \underline{\emph{#3}}}}\\  }
\newcommand{\project}[2]{{ \large{ \underline {\emph{#1}}\hfill #2}}}



\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}

\newcommand{\schoolwithcourses}[6]{
 \textbf{#1 #2} \hfill #3 \\ #4 \\ #5 \\ 
\vspace*{-10pt} #6}


\newcommand{\nanchang}[5]{
 \textbf{#1 #2} \hfill #3 \\ #4 \\ #5}


\newcommand{\school}[4]{
\textbf{#1} #2 $\bullet$ #3\\ 
#4 \\}

% END RESUME DEFINITIONS

\begin{document}
\large{

\smallskip
\vspace*{-45pt}


\vspace*{-10pt}
\begin{center}
{\LARGE \scshape {YU, LIANG} \ \small{www.linkedin.com/in/liangyu2012neu} }
\end{center}
\vspace*{-15pt}

\hspace*{-18pt} \hrulefill

\vspace*{-8pt}

\begin{center}
\small {22 Orient Street, MALDEN, MA $\bullet$ 718-501-0145 $\bullet$ yuliang.name@gmail.com}
\end{center}

\vspace*{-10pt}


\header{Education}
\nanchang{Northeastern University}{- Boston, MA, United States}{2010.9 -- 2012.12}
{College of Computer and Information Science \hfill{GPA 3.54/4.0}}
{Master of Science in Computer Science}

\vspace*{5pt}

\nanchang{Nanchang University}{- Nanchang, Jiangxi, China} {2005.9 -- 2009.6}
{Bachelor of Science in Mathematics \hfill{}}

\vspace*{5pt}
       
\header{Specialties}

\vspace*{-5pt}
\begin{tabbing}
  \hspace{0.1cm}\= \textbf{Operating Systems:} \quad\= Mac OS X, Ubuntu, Cygwin, Windows, iOS, Android\\
              \> \textbf{Languages:}              \> Java, Python, C/C++, Javascript, Flex, SHELL\\
              \> \textbf{Development Tools:}      \> Eclipse, SOAP, REST, Dojo, Ajax, XML, HTML5, Xen\\
              \>                                  \> CSS3, GDB, GIT, SVN, SIP, MySQL, Jenkins, Hadoop

\end{tabbing}


\vspace*{-10pt}


\header{Internship Experience}
\employer{Acme Packet}{2012.1 -- 2012.9}{Software Enginner Intern -- Web service development and testing}
	\begin{achievements}
  \item Configured four virtual machines on XenServe to run SIP tests.
	\item Helped with ASC automated testing framework by writing twenty python tests.
  \item Developed and deployed web services applications with Java, Dojo and GWT/GXT.
	\item Worked on Flex mobile application, fixed bugs and tested it on iPhone and iPad.
  \end{achievements}


\header{Projects and Experience}
\large{ \textbf{Northeastern University Boston, MA\\}
\vspace*{5pt}


\project{Trending Stock Prices via Twitter}{2011.9 -- 2011.12}
  \begin{achievements}
      \item Processed 1.7 billion twitter messages and 50 millions stock records with Hadoop(Pig).
      \item Developed and debugged Java codes in hadoop projects on a ten-node cluster.
  \end{achievements}

\project{Operating System Course}{2011.9 -- 2011.12}
  \begin{achievements}
       \item Experience in multi-processing programming in C.
       \item Wrote c codes to mimic the mirroring, striping, RAID4 and RAID5 operations.
       \item Implemented a file system with basic methods(mkdir, rm, read, write and ls).
  \end{achievements}

\project{Porting MTCP from Linux to Mac OS X 10.6}{2011.1 -- 2011.4}
  \begin{achievements}
       \item Analyzed implementation of MTCP under Linux by reading huge c and c++ codes.
       \item Probed the memory boundaries(stack, heap, data, text) of a process under Mac OS X, by using self-defiled SIGSEGV handler and setlongjump call() in c.
  \end{achievements}

\project{Scientific Community Game(SCG)}{2011.1 -- 2011.4}
  \begin{achievements}
        \item Wrote network-flow avator by using Java, and performanced unit tests to ensure its integration to the existed SCG Arena.
        \item Used Jenkins continuous integration system to ensure the independence of builds and test cases and used EclEmma to measure test coverage in the SCG project.
  \end{achievements}

\project{Server-Client Multi-Users Tank-war Game}{2010.11 -- 2010.12}
  \begin{achievements}
        \item Implemented Java threads to instantly render 2D graphics and sound effect.
        \item Implemented TCP and UDP protocols to establish communication between server and clients.
  \end{achievements}

\vspace*{3pt}

}
\end{document}