%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}


%------------------------------------------------

\cventry
{Tunnel Session Management(TSM) Project} % Job title
{Oracle | Senior (since 2019) Software Engineer in Test} % Organization
{Bedford/Burlington, MA} % Location
{6yr and 9mo. 2014.2 - 2020.11} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Served as the solo test personal in TSM project, the "go-to" person on TSM urgent issues, documented 200+ defects, including critical ones affecting performance and capacity.}
\item {Extended the test coverage of TSM SDK by 5 times and added 1000+ new automation test cases on iOS, Android and Linux platforms, refactored the Tcl scripts into shared library for better reusability.}
\item {Built on-premise testbed with Android phones, iPhones, multiple SBC, 20 Linux VMs across 5 X5-2 Servers and setup Zobbix tool to monitor the network connections and data packets.}
\item {Coordinated resources across QA, Datapath and Application teams to ensure urgent defects were fixed and verifed on schedule, and provided test guidance on customer-reported issues.}
\end{cvitems}
}

\cventry
{SBC Security Team} % Job title
{} % Organization
{} % Location
{} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Tested two factor authenticatons for the configuration-enabled local users together with the factory accounts.}
\item {Configured the remote AAA servers(TACAS+ and Radius) and tested authentication, authorization and accounting features.}
\item {Be the first to write the Tcl scripts to automate the TACACS+ tests and write shell scripts to reproduce the customer’s defect found in performace context.}
\item {Helped the Dev to test the DDOS pretection feature in the SBC product.}
\end{cvitems}
}

\cventry
{SBC Virtualization on private cloud and public cloud} % Job title
{} % Organization
{} % Location
{} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Deployed the virtualized SBC and Linux VMs on the AWS cloud and Azure cloud. }
\item {Integrated the EXFO APIs into the Tcl scripts to decreased the weeks of mannual performance test effort to a couple of days and increased the usage of expensive test equipments in the night time.}
\item {Brought the in-house made Anvil test framework in the public clouds and sovled the library dependency issues. }
\item {Designed the networking diagram for the testbed on the clouds and shared it with tema via the confluence page. }
\item {Did the performance and capacity Tests on the AWS, Azure and VMware platform.}
\item {Tested teh SIP call between the AWS cloud and Azure cloud.}
\end{cvitems}
}


\cventry
{SBC REST Interface} % Job title
{} % Organization
{} % Location
{} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Tracked the work progress in Scrum board in the Agile mode.}
\item {Added hundres of test cases into automation testframe(RAID) to leverate the night time to run the daily regression test.}
\item {Used the Postman App to test SBC Configuration APIs.}
\item {Opened dozens of defects and helped developers to sort out their priorities and fix them.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Topics Android Game Project} % Job title
{Integrated Computer Solutions | Software Developers} % Organization
{Bedford, MA} % Location
{8mo. 2013.4 - 2014.2} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented the APIs in Python and maintained the PostgreSQL database of the Topic Server. }
\item {Leveraged the content provider to save data in SQLite DB and retrieve data to popluate the adapter.}
\end{cvitems} 
}

\cventry
{Inkarus HTML5 and Javascript Game Project} % Job title
{} % Organization
{} % Location
{} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented a function to synchronize the score and screenshot of the winner to Azure Cloud and retrieve
data from the cloud by using WinJS libraray and HTML5.}
\item {Added three advertisement banners in the GameOver page by leveraging the Microsoft Advertising SDK}.
\item {Used the Windows Azure cloud to save the score and screenshot of the solutions and rendered data from cloud to users by using WinJS library and HTML5.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Application Session Controller(ASC) Team} % Job title
{Acme Packet | Software Engineer Intern} % Organization
{Bedford, MA} % Location
{8mo. 2012.1 - 2012.8} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { Developed the Call-Transfer web services application with Java, Dojo and GWT/GXT.}
\item { Worked on Flex mobile application, fixed bugs and tested it on iPhone and iPad.}
\item { Created VMs on the XenServer to run various SIP tests.}
\item { Helped with ASC automated testing framework by wrting twenty Python unit tests on SIP protocol}
\item { Enhanced the quality of an existing iOS mobile application by fixing bugs and improved its UI and workflow by implementing good interface design principles.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Analyzing Company Stock Prices via Twitter Data} % Job title
{Northeastern Univeristy} % Organization
{Boston, MA} % Location
{2ryr. 2010.9 - 2012.12} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Processed 1.7 billions twitter messages and 50 millions stock records with Hadoop.}
\item {Used Pig Scripts to sample of the twitter messages.}
\item {Developed and debugged the program on a ten-node cluster in Java.}
\end{cvitems}
}

\cventry
{Porting MTCP from LInux to Mac OS X 10.6} % Job title
{} % Organization
{} % Location
{} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Analyzed the implementation of MTCP under Linux and listed all the differences in Mac OS X.}
\item {Probed the memory boundaries(stack, heap, data and text sections) of a process under Mac OS X, by using self-defined SIGSEGV handler and setlongjump call() in C.}
\end{cvitems}
}


\cventry
{Simulating Operating System} % Job title
{} % Organization
{} % Location
{} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Experience in mult-processing programming in C.}
\item {Wrote c codes to mimic the mirroring, string, RAID3 and RAID5 operations.}
\item {Implemented a file system with methods like mkdir, rm, read, write and ls.}
\end{cvitems}
}

\cventry
{Scientific Community Game Project} % Job title
{} % Organization
{} % Location
{} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Wrote network-flow avator in Java and wrote unit tests to ensure it can be integrated into the exsited SCG Arena.}
\item {Used Jenkins Continuous Integration System to do the build automation.}
\item {Used EclEmma to measure the test coverage in the SCG project.}
\end{cvitems}
}


\end{cventries}