%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Liang Yu CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{lyu-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

%\lastupdated % Print the Last Updated text at the top right

\namesection{Liang}{Yu}{ % Your name
%\urlstyle{same}\url{http://yuliang.xyz} \\ % Your website, LinkedIn profile or other web address
\href{mailto:yuliang.name@gmail.com}{yuliang.name@gmail.com} | 617.901.0618 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\location{Languages:}
Java \textbullet{} Swift \textbullet{} C \textbullet{} C++\\
Objective-C \textbullet{} Shell Script \\
Python \textbullet{} Tcl \textbullet{} \LaTeX \textbullet{} Ruby\\
\location{Operating System:}
macOS \textbullet{} Linux (CentOS, Red Hat)\\
\location{networking:}
TCP/IP \textbullet{} SIP \textbullet{} Route 53 \\
\textbullet{} RTP \textbullet{} SSL \textbullet{} TLS \\
\location{Web Development:}
Javascript \textbullet{} HTML5 \textbullet{} CSS \textbullet{} RESTful \\
SOAP \textbullet{} Ajax \textbullet{} Bootstrap \textbullet{} MySQL \\ 
\location{Mobile Development:}
iOS \textbullet{} Android \\
\location{Development Tools:}
XCode \textbullet{} Eclipse \textbullet{} Android Studio\\
Visual Studio \textbullet{} GIT \textbullet{} SVN \textbullet{} GDB \\
SIPP \textbullet{} Wireshark \textbullet{} Fiddler \textbullet{} EXFO \\
Pycharm \textbullet{} Window Azure \\
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

%\section{Links} 

%Github:// \href{https://github.com/liangyu}{\bf liangyu} \\
%LinkedIn:\\
%\href{https://www.linkedin.com/in/liangyu8}{\bf www.linkedin.com/in/liangyu8} \\

%\sectionspace % Some whitespace after the section


%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Northeastern University}

\descript{MS in Computer Science}
\location{2010.9 - 2012.12 | Boston, MA}
College of Computer and Information Science

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Nanchang University}

\descript{BS in Mathematics}
\location{2005.9 - 2009.6 | Nanchang, China}
College of Science

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Graduate}

Functional Programming(Scheme) \\
High Performance Computing(C)\\
Advanced Algorithms \\
Computer System(C) \\
Parall Computing in MapReduce(Java) \\
Managing Software Development(Java)

\sectionspace % Some whitespace after the section
%------------------------------------------------
\subsection{Undergraduate}
Assemble Language(IBM X86) \\
Data Structure(C) \\
Intro to Database \\
C Programming Language

\sectionspace % Some whitespace after the section
%----------------------------------------------------------------------------------------
\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
%------------------------------------------------
% Experience
%------------------------------------------------
\section{Experience}
\runsubsection{Oracle}
\descript{| Software Testing Engineer}
\location{2014.2 – recent | Bedford, MA}
\textbf{TSM Project (Linux, iOS, Android platforms)}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Enhanced the exsited iOS/Linux apps to test new features and maintained the existed Android Test App.
\item Wrote scripts to automate more than 1,000 test cases for TSM SDK, which extended the test coverage 5 times. 
\item Raised 200+ product defects, including critical defects that affected performance and capacity.
\item Familiar with TLS/SSL protocols and socket programming in Linux.
\item Design test plan documents and executed the capacity and performance tests.
\end{tightitemize}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\textbf{SBC REST API Project}
\begin{tightitemize}
\item Worked in an Agile Team and wrote automatic scripts to test SBC API and opened dozens of defects.
\end{tightitemize}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\textbf{SBC VNF Project}
\begin{tightitemize}
\item Wrote TCL scripts to automate various performance test cases, which covered different vm core combinations.
\item Released the weeks of mannual test effort and boosted the usage of test equipments.
\end{tightitemize}
\sectionspace % Some whitespace after the section
%------------------------------------------------
\runsubsectionnormal{Integrated Computer Solutions}
\descriptbold{| Software Developer}

\location{2013.4 – 2014.2 | Bedford, MA}
\textbf{Topics (Android App)}
\begin{tightitemize}
\item Used AsyncTask class to call the Restful API and parsed the reponses in JSON format.
\item Implemented unit tests with pytest in Ubuntu environment.
\end{tightitemize}

\vspace{2 mm}
\textbf{Inkarus Game (Window 8 Metro Apps)}
\begin{tightitemize}
\item Integrated existing App with the Microsoft Advertising SDK.
\item Implemented the feature to synchronize the score and screenshot of the solution to Windows Azure cloud and retrieve data from cloud by using WinJS libraray and HTML5.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsectionnormal{Acme Packet}
\descriptbold{| Software Developer Intern}

\location{2012.1 – 2012.8 | Bedford, MA}
\begin{tightitemize}
\item Contributed to ASC automated testing framework by writing unit tests in Python.
\item Wrote JavaScript to develop a Call-Transfer web service application with SOAP API.
\item Configured VMs on XenServer to run various SIP tests.
\item Enhanced an existed iOS App by fixing defects and verified them on iPhone and iPad. 
\item Fixed defects in existed web services applications.
\end{tightitemize}

\runsubsectionnormal{Personal Project}
\descriptbold{| iOS App Developer}

\location{theBostonT: avaiable in Apple App Store}
\begin{tightitemize}
\item Utilized the REST API provided by MTBA to get real-time data.
\item Familiar with Corelocation, Mapkit, Network frameworks, UITableView and UICollectionView.
\item Implemented design patterns to maintain clean and clean codes.
\item Used GitHub for source control.
\end{tightitemize}

%\location{FlightRadar 24 app for Boston Plane Spotting}
%\begin{tightitemize}
%\item TBD
%\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Societies
%------------------------------------------------
\section{SOCIETIES} 

\begin{tabular}{l}
\textbullet{} Private Pilot\\
\end{tabular}

\sectionspace % Some whitespace after the section
%----------------------------------------------------------------------------------------
\end{minipage} % The end of the right column
%----------------------------------------------------------------------------------------
\end{document}
