%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Liang Yu CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{lyu-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

%\lastupdated % Print the Last Updated text at the top right

\namesection{Liang}{Yu}{
\href{mailto:yuliang.name@gmail.com}{yuliang.name@gmail.com} | 617.901.0618
}


%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%

\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
%------------------------------------------------
% Experience
%------------------------------------------------
\section{Experience}
\runsubsection{Oracle}
\descript{| Senior Software Testing Engineer}
\location{2014.2 – 2020.11 | Bedford, MA}
\textbf{TSM Project (Linux, iOS, Android platforms)}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Enhanced the exsited iOS/Linux apps to test new features and maintained the existed Android Test App.
\item Wrote scripts to automate more than 1,000 test cases for TSM SDK. It extended the test coverage by 5 times. 
\item Raised 200+ product defects, including critical defects that affected performance and capacity.
\item Familiar with TLS/SSL protocols and socket programming in Linux.
\item Design test plan documents and executed the capacity and performance tests with shell scripts and EXFO.
\end{tightitemize}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\textbf{SBC REST API Project}
\begin{tightitemize}
\item Worked in an Agile Team and wrote automatic scripts to test SBC API and opened dozens of defects.
\item Used the scrum board to track the work progress
\end{tightitemize}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\textbf{SBC VNF Project}
\begin{tightitemize}
\item Wrote Tcl scripts to automate various performance test cases, which covered different combinations of signaling, forwarding, DOS cores.
\item Decreased the weeks of mannual test effort to a couple of days and increased the usage of test equipments in the night time.
\end{tightitemize}
\sectionspace % Some whitespace after the section

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\textbf{Cloud SBC Project}
\begin{tightitemize}
\item Deployed the virtual SBCs and Linux VMs on the AWS cloud and Azure cloud. 
\item Designed the test networking framework on the clouds
\item Installed the in-house made Anvile Testframe on those Linux VMs and solved the library dependency issues.
\item Performed Capacity Tests on the AWS and Azure platform 
\item Tested the calling between the AWS cloud and Azure cloud.
\end{tightitemize}
\sectionspace % Some whitespace after the section

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\textbf{Hardware SBC Project}
\begin{tightitemize}
\item DDOS preventing test
\item Remote authentication and authorization tests with AAA servera
\item Test
\item 
\item 
\end{tightitemize}
\sectionspace % Some whitespace after the section

%------------------------------------------------
\runsubsectionnormal{Integrated Computer Solutions}
\descriptbold{| Software Developer}

\location{2013.4 – 2014.2 | Bedford, MA}
\textbf{Topics (Android App)}
\begin{tightitemize}
\item Used AsyncTask class to call the Restful API and parsed the reponses in JSON format.
\item Implemented unit tests with pytest in Ubuntu environment.
\end{tightitemize}

\vspace{2 mm}
\textbf{Inkarus Game (Window 8 Metro Apps)}
\begin{tightitemize}
\item Integrated existing App with the Microsoft Advertising SDK.
\item Implemented the feature to synchronize the score and screenshot of the solution to Windows Azure cloud and retrieve data from cloud by using WinJS libraray and HTML5.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsectionnormal{Acme Packet}
\descriptbold{| Software Developer Intern}

\location{2012.1 – 2012.8 | Bedford, MA}
\begin{tightitemize}
\item Contributed to ASC automated testing framework by writing unit tests in Python.
\item Wrote JavaScript to develop a Call-Transfer web service application with SOAP API.
\item Configured VMs on XenServer to run various SIP tests.
\item Enhanced an existed iOS App by fixing defects and verified them on iPhone and iPad. 
\item Fixed defects in existed web services applications.
\end{tightitemize}

\runsubsectionnormal{Personal Project}
\descriptbold{| iOS App: theBostonT}

\location{2017}
\begin{tightitemize}
\item Retrieved the real-time traffic data via the REST API provided by Boston MTBA.
\item Familiar with iOS framework, like Corelocation, Mapkit, Network, UITableView and UICollectionView.
\item Implemented design patterns to maintain clean and clean codes.
\item Used GitHub for source control.
\end{tightitemize}

\sectionspace % Some whitespace after the section
%----------------------------------------------------------------------------------------
\end{minipage} % The end of the right column
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\location{Languages:}
Java \textbullet{} Swift \textbullet{} C \textbullet{} C++\\
Objective-C \textbullet{} Shell \textbullet{} Lisp \\
Python \textbullet{} Tcl \textbullet{} \LaTeX \textbullet{} Ruby\\

\vspace{2 mm}

\location{Operating System:}
macOS \textbullet{} CentOS \textbullet{} Red Hat \\

\vspace{2 mm}

\location{networking:}
TCP/IP \textbullet{} SIP \textbullet{} Route 53 \\
\textbullet{} RTP \textbullet{} TLS/SSL \textbullet{} IPSec \\
SIPP \textbullet{} Wireshark \textbullet{} Fiddler \textbullet{} EXFO \\

\vspace{2 mm}

\location{Web Development:}
REST \textbullet{} SOAP \textbullet{} Javascript \\
HTML5 \textbullet{} CSS \textbullet{} Ajax \\ 
Bootstrap \textbullet{} MySQL \\ 

\vspace{2 mm}

\location{Mobile Development:}
iOS \textbullet{} XCode \textbullet{} SwiftUI \\ 
Android \textbullet{} Android Studio \\

\vspace{2 mm}

\location{Cloud and Virtulization Platforms:}
AWS \textbullet{} Microsoft Azure \textbullet{} VMware ESXi \\

\vspace{2 mm}

\location{Development Tools:}
GIT \textbullet{} SVN \textbullet{} Eclipse \\
Visual Studio \textbullet{} Pycharm \textbullet{} GDB \\
\sectionspace % Some whitespace after the section


%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Northeastern University}

\descript{MS in Computer Science}
\location{2010.9 - 2012.12 | Boston, MA}
College of Computer and Information Science

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Nanchang University}

\descript{BS in Mathematics}
\location{2005.9 - 2009.6 | Nanchang, China}
College of Science

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Graduate}

Program Design Paradigms in Lisp \\
Advanced Algorithms \\
High Performance Computing(C)\\
Computer System(C) \\
Parall Computing in MapReduce(Java) \\
Managing Software Development(Java)

\sectionspace % Some whitespace after the section
%------------------------------------------------
\subsection{Undergraduate}
Assemble Language(IBM X86) \\
C Programming Language \\
Data Structure in C \\
Introduction to Database

\sectionspace % Some whitespace after the section
%----------------------------------------------------------------------------------------
\end{minipage} % The end of the left column
\hfill


\end{document}
