%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Liang Yu CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{lyu-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

%\lastupdated % Print the Last Updated text at the top right

\namesection{Liang}{Yu}{ % Your name
%\urlstyle{same}\url{http://yuliang.xyz} \\ % Your website, LinkedIn profile or other web address
\href{mailto:yuliang.name@gmail.com}{yuliang.name@gmail.com} | 617.901.0618 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\location{Languages:}
Java \textbullet{} Swift \textbullet{} C \textbullet{} C++\\
Objective-C \textbullet{} Shell \textbullet{} Lisp \\
Python \textbullet{} Tcl \textbullet{} \LaTeX \textbullet{} Ruby\\

\vspace{2 mm}

\location{Operating System:}
macOS \textbullet{} CentOS \textbullet{} Red Hat \\

\vspace{2 mm}

\location{networking:}
TCP/IP \textbullet{} SIP \textbullet{} EXFO  \\
\textbullet{} RTP \textbullet{} TLS/SSL \textbullet{} IPSec \\
SIPP \textbullet{} Wireshark \textbullet{} Fiddler \\

\vspace{2 mm}

\location{Web Development:}
REST \textbullet{} SOAP \textbullet{} Javascript \\
HTML5 \textbullet{} CSS \textbullet{} Ajax \\ 
Bootstrap \textbullet{} MySQL \\ 

\vspace{2 mm}

\location{Mobile Development:}
iOS \textbullet{} XCode \textbullet{} SwiftUI \\ 
Android \textbullet{} Android Studio \\

\vspace{2 mm}

\location{Cloud and Virtulization Platforms:}
AWS \textbullet{} Microsoft Azure \textbullet{} VMware ESXi \\

\vspace{2 mm}

\location{Development Tools:}
GIT \textbullet{} SVN \textbullet{} Eclipse \textbullet{} Postman \\
Visual Studio \textbullet{} Pycharm \textbullet{} GDB \\
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

%\section{Links} 

%Github:// \href{https://github.com/liangyu}{\bf liangyu} \\
%LinkedIn:\\
%\href{https://www.linkedin.com/in/liangyu8}{\bf www.linkedin.com/in/liangyu8} \\

%\sectionspace % Some whitespace after the section


%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Northeastern University}

\descript{MS in Computer Science}
\location{2010.9 - 2012.12 | Boston, MA}
College of Computer and Information Science

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Nanchang University}

\descript{BS in Mathematics}
\location{2005.9 - 2009.6 | Nanchang, China}
College of Science

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Graduate}

Program Design Paradigms in Lisp \\
Advanced Algorithms \\
High Performance Computing(C)\\
Computer System(C) \\
Parall Computing in MapReduce(Java) \\
Managing Software Development(Java)

\sectionspace % Some whitespace after the section
%------------------------------------------------
\subsection{Undergraduate}
Assemble Language(IBM X86) \\
C Programming Language \\
Data Structure in C \\
Introduction to Database

\sectionspace % Some whitespace after the section
%----------------------------------------------------------------------------------------
\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
%------------------------------------------------
% Experience
%------------------------------------------------
\section{Experience}
\runsubsection{Oracle}
\descript{| Senior Software Engineer in Test}
\location{2014.2 – 2020.11 | Bedford, MA}
\textbf{TSM Project (Linux, iOS, Android platforms)}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Enhanced the exsited iOS/Linux apps to test new features and maintained the existed Android Test App.
\item Wrote scripts to automate more than 1,000 test cases for TSM SDK. It extended the test coverage by 5 times. 
\item Raised 200+ product defects, including critical defects that affected performance and capacity.
\item Familiar with TLS/SSL protocols and socket programming in Linux environment.
\item Designed test plan documents and executed the capacity and performance tests with shell scripts and EXFO.
\end{tightitemize}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\textbf{SBC REST API Project}
\begin{tightitemize}
\item Used the scrum board to track the work progress in the Agile mode.
\item Added hundreds of test cases into the RAID automation Testframe so that regression test can be done in the night time.
\item Used the Postman to test SBC APIs.
\item opened dozens of defects.
\end{tightitemize}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\textbf{Virtualized SBC on private cloud and public cloud}
\begin{tightitemize}
\item Integrated the EXFO APIs into the Tcl script to automate various performance test cases that would otherwise be repeated for different CPU core combinations(signaling, forwarding, Transcodeing or DOS cores).
\item Decreased the weeks of mannual test effort to a couple of days and increased the usage of expensive test equipments in the night time.
\item Deployed the virtual SBCs and Linux VMs on the AWS cloud and Azure cloud. 
\item Designed the networking diagram for the testbed on the clouds and documented it on the confluence page.
\item Installed the in-house made Anvil Testframe on those Linux VMs and solved the library dependency issues.
\item Performed Capacity Tests on the AWS and Azure platform 
\item Tested the SIP call between the AWS cloud and Azure cloud.
\item Tested the DDOS protection feature in the SBC
\item Executed tests related to authentication and authorization and accounting with remote AAA servers (TACACS+ and Radius).
\end{tightitemize}

\sectionspace % Some whitespace after the section
%------------------------------------------------
\runsubsectionnormal{Integrated Computer Solutions}
\descriptbold{| Software Developer}

\location{2013.4 – 2014.2 | Bedford, MA}
\textbf{Topics (Android App)}
\begin{tightitemize}
\item Used AsyncTask class to call the Restful API and parsed the reponses in JSON format.
\item Implemented unit tests with pytest in Ubuntu environment.
\end{tightitemize}

\vspace{2 mm}
\textbf{Inkarus (Javascript Game on Windows Tablet)}
\begin{tightitemize}
\item Integrated existing App with the Microsoft Advertising SDK.
\item Implemented the feature to synchronize the score and screenshot of the solution to Windows Azure cloud and retrieve data from cloud by using WinJS libraray and HTML5.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
\runsubsectionnormal{Acme Packet}
\descriptbold{| Software Developer Intern}

\location{2012.1 – 2012.8 | Bedford, MA}
\begin{tightitemize}
\item Contributed to ASC automated testing framework written in Python.
\item Developed a Call-Transfer web service application with SOAP API and Javascript.
\item Configured VMs on XenServer to run various SIP tests.
\end{tightitemize}

%-------------Optional--------------------------
%\runsubsectionnormal{Freelancer Project}
%\descriptbold{| iOS App: theBostonT}

%\location{2017}
%\begin{tightitemize}
%\item Retrieved the real-time traffic data via the REST API provided by Boston MTBA.
%\item Familiar with iOS framework, like Corelocation, Mapkit, Network, UITableView and UICollectionView.
%\item Implemented design patterns to maintain clean and clean codes.
%\item Used GitHub for source control.
%\end{tightitemize}


\sectionspace % Some whitespace after the section
%----------------------------------------------------------------------------------------
\end{minipage} % The end of the right column
%----------------------------------------------------------------------------------------
\end{document}
